\vspace{-3em} \textbf{ Mapping stellar surfaces\\ II: An interpretable Gaussian process model for light curves }

### 2021-02-04 paper2/ms.tex
more acks

We would like to thank David W. Hogg, Michael Gully-Santiago, Adam Jermyn,
Megan Bedell, and the
Astronomical Data Group at the Center for Computational Astrophysics for
many thought-provoking discussions that helped shape this paper.

>>>>

We would like to thank David W. Hogg, Michael Gully-Santiago, Adam Jermyn,
Megan Bedell, Will Farr, Dylan Simon, and the
Astronomical Data Group at the Center for Computational Astrophysics for
their help and for
many thought-provoking discussions that made this paper possible.
